2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
commit changes to qmd file

### Interpretation of Polling Averages by State

@@

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

#pp_check(first_model) +
  #theme_classic() +
  #theme(legend.position = "bottom")

#posterior_vs_prior(first_model) +
 # theme_minimal() +
  #scale_color_brewer(palette = "Set1") +
 # theme(legend.position = "bottom") +
  #coord_flip()
```

>>>>

## Interpretation of Polling Averages by State

@@
